### 2015-07-15 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/Manual_coupling_AxiSEM_Specfem3D.tex
Buildbot ran the code beautifier.
Change Axisem coupling manual

\noindent It generate mesh files (on 1 proc on Curie), and copy files 'list\_gll\_boundary\_spherical.txt' and 'list\_gll\_boundary\_cartesian.txt' in AxiSEM solver dir

\noindent Also, check Meshfem3D with parameters :

@@

\item[\textbullet] In the directory MESH/ :

@@

\item[\textbullet] ParFileMeshChunk  : parameters for the chunk meshing

\item[\textbullet] iasp91\_dsm or prem\_dsm : background model used in both AxiSEM ans Specfem3D

\item[\textbullet] In the Directory DATA/

\item[\textbullet] CMTSOLUTION  : with 0 in order to not use source inside

\item[\textbullet] coeff\_poly\_deg12 : to generate smooth intitial solution

\item[\textbullet] STATIONS  : stations files

\item[\textbullet] Par\_file : with

\item[\textbullet] SIMULATION\_TYPE=1

\item[\textbullet] SAVE\_FORWARD = .false.

\item[\textbullet] COUPLE\_WITH\_EXTERNAL\_CODE = .true

\item[\textbullet] EXTERNAL\_CODE\_TYPE    = 2

>>>>

\noindent It generate mesh files (on 1 proc on Curie), and copy files 'list\_gll\_boundary\_spherical.txt' and 'list\_gll\_boundary\_cartesian.txt' in AxiSEM solver dir.

\bigskip
\medskip

\noindent Also, check Meshfem3D with parameters $\Longrightarrow$ In the directory MESH/ :

@@

\item[\textbullet] 'ParFileMeshChunk'  : parameters for the chunk meshing

\item[\textbullet] 'iasp91\_dsm' or 'prem\_dsm' : background model used in both AxiSEM ans Specfem3D

\noindent In the Directory DATA/ :

@@

\item[\textbullet] 'CMTSOLUTION'  : with 0 in order to not use source inside

\item[\textbullet] 'coeff\_poly\_deg12' : to generate smooth intitial solution

\item[\textbullet] 'STATIONS'  : stations files

\item[\textbullet] Set the file 'Par\_file' with these parmeters :

\begin{itemize}
\item[\textbullet] SIMULATION\_TYPE=1
\item[\textbullet] SAVE\_FORWARD = .false.
\item[\textbullet] COUPLE\_WITH\_EXTERNAL\_CODE = .true
\item[\textbullet] EXTERNAL\_CODE\_TYPE    = 2
\end{itemize}
